Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
Fixing minor errors in PS2 results section.

\subsubsection{Results}
Table \ref{tbl:prestudy2} displays the raw results of the process just described.  A number of features were quite striking about the data. First, while most of the data records were small and relatively simple, nearly one in each category produced substantially more complex records than the rest; in particular, Amazon, Soundcloud, Twitter and Weather Underground stood out in their respective categories.

Looking at equivalent properties, we found overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones in common with others.  While some of these `unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties that were simply absent.  Only one Spotify, among music providers, included information about the album(s) featuring a given song.  Such omissions show us that these data APIs reflect each provider's own specific capabilities and needs, and suggests that integrating information from multiple sources may allow more complete and useful representations to be assembled.

@@

Although not included in the table above, we also examined the source schemas of many of the data sources for property enumerated type values.  There was substantial terminological inconsistency among such values, but also cases where some sources had values not represented in the other source's sets.  For example, the property ``Gender''  on Facebook allowed only supported ``Male'' and ``Female'' for values, while Google+ included a third option,``other''.  ``Relationship status'' was another which was similarly complex. None of the string representations of enumerated value sets matched across data sources perfectly.

>>>>

\subsubsection{Results}
Table \ref{tbl:prestudy2} shows the raw results of the process described.  A number of features were quite striking about the data; First, while most of the data records were small and relatively simple, nearly one in each category produced substantially more complex records than the rest. In particular, Amazon, Soundcloud, Twitter and Weather Underground stood out in their respective categories.

Looking at equivalent properties, we found overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones in common with others.  While some of these `unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties that were simply absent.  Only Spotify, out of the 4 music providers, included information about the album(s) featuring a given song.  Such omissions show us that these data APIs reflect each provider's own specific capabilities and needs, and suggests that integrating information from multiple sources may allow more complete and useful representations to be assembled.

@@

Although not included in the table above, we also examined the source schemas of many of the data sources for property enumerated type values.  There was substantial terminological inconsistency among such values, but also cases where some sources had values not represented in the other source's sets.  For example, the property ``gender''  on Facebook allowed only supported ``male'' and ``female'' for values, while Google+ included a third option,``other''.  ``Relationship status'' was another which was similarly complex, as none of the string representations of enumerated value sets matched across data sources perfectly.
